Predicting FOMC Actions using ML and NLP

### 2019-04-25 presentation/paper.tex
paper

 \item We test the accuracy of ML models trained on FOMC statements and a percentage of FOMC minutes on a test set of FOMC minutes
 \item We create a predictive model that is trained on documents that are temporally released before the test document.  Typically we will test with FOMC minutes releases or Board of Governor speeches.  
\end{enumerate}

@@

When we train the model with statements and minutes, ten statements will be considered one document because of the magnitude of minute size to statement size.

>>>>

 \item We test the accuracy of ML models trained on a random mixture of FOMC minutes, speeches, and statements on a test set of FOMC documents.  In this stage, we are determining the viability of ML methods in predicting FOMC action on test documents, and we will evaluate the model accuracy with precision and recall.  The models are: 
 \begin{itemize}
    \item Naive Bayes
    \item Logistic Regression 
    \item SVM
    \item Logistic Lasso
 \end{itemize}
 \item We create a predictive model that is trained on documents that are temporally released before the test document.  Typically we will test with FOMC minutes releases or Board of Governor speeches that are temporally released after the training documents. 
 \item  
\end{enumerate}

@@
